---
title: "HW7"
author: "Valerie"
date: "4/5/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Recall the NHANES dataset that we used in Lesson 10. 

1. In the dataset there is a discrete variable called SleepTrouble indicating whether each participant has trouble sleeping or not. You are going to build a set of classifiers for this dependent variable. You may use any (set of) independent variable(s) you like except for the variable callsed SleepHrsNight. 

For each of the model types (null model, logistic regression, decision tree, random forest, k-nearest neighbor) do the following:

1A. Build the classifier.

1B. Report its effectiveness on the NHANES dataset.

1C. Make an appropriate visualization of this model.

1D. Interpret the results. What have you learned about people's sleeping habits?

2. Repeat problem 1 except now you are to use the quantitative variable called SleepHrsNight. The model types are as follows: null model, multiple regression, regression tree, random forest.

Link to repository:[https://github.com/valerie-mac/Lesson11.git]
```{r}
#Loading packages
library(tidyverse)
library(class)
library(rpart)
library(NHANES)
library(RColorBrewer)
library(plot3D)
library(parallel)
library(randomForestSRC)
library(ggRandomForests)
library(mosaic)
library(dplyr)
```

```{r}
# Create the "people"" dataset from NHANES 
people <- NHANES %>% dplyr::select(Gender, Age, Marijuana, BMI, SexNumPartnLife, SleepTrouble) %>% na.omit(people)
```


```{r}
glimpse(people)
```


```{r}
# Convert factors to numeric
people$Gender <- as.numeric(people$Gender)
people$Age <- as.numeric(people$Age)
people$Marijuana <- as.numeric(people$Marijuana)
people$BMI <- as.numeric(people$BMI)
people$SexNumPartnLife <- as.numeric(people$SexNumPartnLife)
people$SleepTrouble <- as.numeric(people$SleepTrouble)

people <- na.omit(people)
```


```{r}
# Apply knn procedure to predict SleepTrouble

# Let's try different values of k to see how that affects performance
knn.1 <- knn(train = people, test = people, cl = (people$SleepTrouble), k = 1)
knn.3 <- knn(train = people, test = people, cl = people$SleepTrouble, k = 3)
knn.5 <- knn(train = people, test = people, cl = people$SleepTrouble, k = 5)
knn.20 <- knn(train = people, test = people, cl = people$SleepTrouble, k = 20)

#knn.1

```
Now let's see how well it classifies

```{r}

# Calculate the percent predicted correctly

100*sum(people$SleepTrouble == knn.1)/length(knn.1)
100*sum(people$SleepTrouble == knn.3)/length(knn.3)
100*sum(people$SleepTrouble == knn.5)/length(knn.5)
100*sum(people$SleepTrouble == knn.20)/length(knn.20)

```

```{r}
# Another way to look at success rate against increasing k

table(knn.1, people$SleepTrouble)
table(knn.3, people$SleepTrouble)
table(knn.5, people$SleepTrouble)
table(knn.20, people$SleepTrouble)
```

```{r}

# Create the grid

ages <- range(~ Age, data = people)
genders <- range(~ Gender, data = people)
marijuanas <- range(~Marijuana, data= people)
sexnumpartnlifes <- range(~SexNumPartnLife, data=people)
bmis <- range (~BMI, data=people)
res <- 100
fake_grid <- expand.grid(
  Age = seq(from = ages[1], to = ages[2], length.out = res),
  Gender = seq(from = genders[1], to = genders[2], length.out = res))
  Marijuana = seq(from = marijuanas[1], to = marijuanas[2], length.out = res)
  BMI= seq(from = bmis[1], to = bmis[2], length.out = res)
  SexNumPartnLife = seq(from = sexnumpartnlifes[1], to = sexnumpartnlifes[2], length.out = res)
#Get the overall proportion, p, of people with sleep trouble
```
```{r}
p <- sum(people$SleepTrouble == 1)/length(people$SleepTrouble)
```
```{r}
# Null model prediction

pred_null <- rep(p, nrow(fake_grid))
```
```{r}
# Reinitializing people back to orginal coding with Sleep Trouble as Yes and No
people <- NHANES %>% 
  dplyr::select(Age, Gender, Marijuana, BMI, SexNumPartnLife, SleepTrouble) %>% 
  na.omit(people)

form <- as.formula("SleepTrouble ~ Age + Gender + BMI + Marijuana + SexNumPartnLife")
```
```{r}
# Evaluate each model on each grid point
# For the decision tree

dmod_tree <- rpart(form, data = people, 
                   control = rpart.control(cp = 0.005, minbucket = 30))
```
# For the forest
```{r}
set.seed(10000)
#dmod_forest <- rfsrc(form, data = people, 
#                     ntree = 201, mtry = 3)
# try with randomForest instead of randomForestSRC package
library(randomForest)
```

```{r}
dmod_forest <- randomForest(form, data = people, 
                     ntree = 201, mtry = 2)
```
This is where I stopped. I had gone past this previously, commenting out the non-working sections, ut had to start over because the code was too hairy. This is just where I am on this attempt.

```{r}
#Generating predictions for tree and forest
#pred_tree <- predict(dmod_tree, newdata = fake_grid)[, 1]
#pred_forest <- predict(dmod_forest, newdata = fake_grid, 
#                       type = "prob")[, "Yes"]
```

```{r}
# K-nearest neighbor prediction
#pred_knn <- people %>%
  #select(Age, Gender, BMI, Marijuana, SexNumPartnLife) %>%
  #knn(test=select(fake_grid, Age, Gender, BMI, Marijuana, SexNumPartnLife), cl = people$SleepTrouble, k=5) 

```
